\documentclass[]{kyvernitis-resume}
\usepackage{enumitem}
\usepackage{comment}

\fullname{Hamidreza Kouchakzadeh}
 \jobtitle{Backend Developer}

\begin{document}
\resumeheader
{\linkedin{hamidreza-kouchakzadeh}}
{\email{hamidrezakouchakzadeh@gmail.com}}
{\github{MrHamid78}}
{\phone{+98 9330243474}}
{\address{Karaj, Alborz Province, Iran}}
{\nationality{Iranian}}

\begin{section}{About me}
Experienced PHP developer with a deep understanding of the language and its ecosystem. Proficient in building robust web applications and implementing complex features using PHP and frameworks like Symfony. Skilled in database management with MySQL and proficient in front-end technologies such as HTML, CSS, JavaScript, and jQuery. Detail-oriented and dedicated to writing clean, efficient, and maintainable code. Continuously learning and staying updated with the latest PHP trends and best practices. Committed to delivering high-quality solutions and providing excellent user experiences.
\end{section}


\begin{section}{Work Experience}
    \begin{subsection}{PEP Co.}{Software Developer}{June 2022 -- PRESENT}{Tehran, Iran}{(Electronic Payment Services)}



%		\item Subsidiary of Pasargad Bank, specializing in electronic payment services.
%		\item Gained experience working with large-scale software systems within the company.

%		\item Also worked with Angular framework in the front-end development as per project requirements.
%		\item Familiarized myself with Agile methodologies and worked with Elasticsearch and RabbitMQ for request queue management.
%		\item Contributed to several projects within the company, including:
		
%		\begin{itemize}[label={}, leftmargin=1cm]
%		  \item Internet Payment Gateway (IPG): Developed and maintained an online payment gateway system.
%		  \item Traffic Violations System: Worked on the development and enhancement of a system for managing traffic violations.
%		  \item Feeda (Foreigners' Unique Code): Participated in the development of a system for generating unique codes for foreigners.
%		  \item Seta (Special Invoice Generation System): Collaborated on the creation of a specialized invoice generation system.
%		\end{itemize}
		\item Developed and maintained large-scale software systems.
%		\item Integrated and managed third-party services, such as Elasticsearch and RabbitMQ, for data retrieval and messaging.
		\item Developed the Smart Refund System : Contributed to the creation of a robust system for handling automated refunds, which improved efficiency and reduced manual errors in transaction processing.
		\item Enhanced PEPCO's CRM System : Collaborated on the development and enhancement of the CRM system, improving customer data management and interactions.
		\item Implemented a CI/CD Pipeline :
			\begin{itemize}
				\item Designed and set up a continuous integration and continuous deployment (CI/CD) pipeline using Jenkins, automating the build and deployment process.
				\item Reduced deployment time by 50\%, enabling developers to focus more on coding and less on manual deployment tasks.

			\end{itemize}

		\item Developed Custom Libraries and Tools:
			\begin{itemize}
				\item Created reusable libraries and tools to streamline development across various projects.
				\item Implemented automated performance logging, which provided valuable insights into system performance and aided in code optimization.
			\end{itemize}

		\item Automated Testing:
			\begin{itemize}
				\item Implemented automated testing for both frontend and backend components using Selenium , junit \& mockito.
				\item For frontend testing, utilized Selenium to automate browser interactions and validate user interfaces, ensuring consistent and bug-free user experiences.
				\item Applied similar automation strategies to backend services, enhancing the reliability and functionality of the software across different components.
			\end{itemize}

		\item Utilized Angular for Front-End Development:
			\begin{itemize}
				\item Applied Angular framework for front-end development based on project needs, enhancing user interface and user experience.
			\end{itemize}


		\item Developed a Performance Logging Library Using the ELK Stack:
			\begin{itemize}
			\item  Created a custom library to integrate with the ELK Stack for automated performance logging.
			\item  This library provided valuable insights into system performance, facilitating real-time monitoring and historical analysis.
			\item  The implementation of this library significantly enhanced the ability to optimize code and improve system efficiency by identifying performance bottlenecks.
			\end{itemize}


    \end{subsection}

\hfill

 \begin{subsection}{RIECO.}{Software Developer  \& Technical Project Coordinator}{Dec 2020-- Nov 2021}{Alborz, Iran}{(B2B Software Solutions)}
 %      	\item Specialized in the development and production of software solutions for the oil and gas industry.
%	\item Developed maintenance software, Integrated Decision-Making Systems (IDMS), and Engineering Document Control Software (EDMS).
%	\item Collaborated with major engineering companies such as Rampco, Persian gulf petrochemical industries , and Apadana Petrochemical, providing them with our software solutions.
%	\item Focused on studying software design patterns, particularly MVC, to meet the complexity of projects.
%	\item Conducted back-end development using PHP, Symfony libraries, and MySQL database ; also Implemented Redis caching for improved performance.
%	\item Contributed to a parallel project using Golang, ensuring its integration with our main software.
%	\item Coordinated the work of the programming team with other departments.
	\item Backend Development:
		\begin{itemize}
			\item Developed and maintained B2B software solutions including Integrated Decision-Making Systems (IDMS), Business Process Management Systems (BPMS), and Engineering Document Management Systems (EDMS).
		\end{itemize}

	\item Technical Project Coordination:
		\begin{itemize}
			\item Acted as a key liaison between customers and the development team, gathering requirements and ensuring their accurate translation into actionable tasks.
			\item Coordinated technical efforts, managed project timelines, and facilitated communication between stakeholders and the development team.
		\end{itemize}

	\item Business Process Management System (BPMS) Design:
		\begin{itemize}
			\item Designed and implemented a BPMS that streamlined development processes and reduced time-to-delivery.
			\item Enabled operators to manage and automate common services, enhancing operational efficiency and reducing the time required to fulfill customer demands.
		\end{itemize}
	
	\item Customer and Team Management:
		\begin{itemize}
			\item Engaged with customers to understand their needs and translate these into technical requirements for the development team.
			\item Managed the technical team’s tasks, ensuring alignment with project goals and customer expectations.
		\end{itemize}
	
	\item Process Optimization:
		\begin{itemize}
			\item Improved development workflows and system functionality by integrating reusable components and optimizing processes.
		\end{itemize}
    \end{subsection}
    
    \begin{subsection}{Koleh Poshti}{Project Manager \& Full-Stack Developer}{Dec 2019 -- July 2020}{Alborz, Iran}{(Tourism Industry)}

        	\item Project Management:
	\begin{itemize}
	\item Managed and led a software project focused on developing a customized tour platform for the Turkish tourism market.
	\item Coordinated project timelines, delegated tasks, and ensured that deliverables met quality standards and deadlines.
	\item Collaborated with stakeholders and the development team to define project scope, goals, and deliverables.
	\end{itemize}

        	\item Backend Development:
	\begin{itemize}
	\item Developed and maintained backend systems.
	\item Implemented features that allowed for customized tour packages, streamlining the booking process.
	\item Integrated payment gateways and third-party APIs to facilitate seamless transactions and data exchange.
	\end{itemize}

        	\item Investor Relations:
	\begin{itemize}
	\item Contributed to the development of business strategies to ensure the startup’s growth and sustainability.
	\end{itemize}

        	\item Collaboration \& Communication:
	\begin{itemize}
	\item Acted as a bridge between technical and non-technical stakeholders, translating business needs into technical specifications.
	\item Facilitated clear communication across different teams, ensuring alignment and a cohesive approach to project development.
	\end{itemize}


%        	\item Worked in the tourism industry for Koleh Poshti, a company specializing in organizing outbound tours.
%	\item Managed and implemented a software project for customized tours in Turkey, where customers could personalize their travel experiences from accommodation to specific destinations and activities during their stay.
%	\item The project received investment and support from 100 Startups, a capital investment event, and later secured funding from NovinTech.
%	\item Unfortunately, due to the COVID-19 pandemic and the economic challenges that impacted society, the startup was forced to halt operations.
%	\item Utilized PHP and MySQL database for the project development in Koleh Poshti.
%	\item Familiarized myself with the WordPress platform to facilitate the migration of the company's previous website to the new system.
%	\item Engaged in business aspects of the company, collaborating with Zavie to attract investors.
    \end{subsection}

\hfill

    \begin{subsection}{Javanpardaz Alborz}{Project-based Work}{Oct 2016 - June 2017}{Alborz, Iran}{(Real Estate Financial Management)}
	\item Engaged in a project at Javanpardaz Alborz, primarily focusing on the development of the Sama software (abbreviated as "Sandogh-e Mekanize Amlak" in Persian), which was a real estate management system.
	\item \textbf{ Developed Real Estate Management Software: }
	\begin{itemize}
	\item Built a system for financial calculations and property management.
	\item Developed a website using PHP for registering and purchasing licenses.
	\item Created a C\# desktop application integrated with the serverside application for asynchronous data synchronization and client data backup.
	\end{itemize}
%	\item Acquired proficiency in C\# programming language and utilized Telerik components to design the relevant Windows forms.
%	\item The workflow of the software involved calculating commissions for real estate consultants in each transaction and generating invoices for the parties involved. Additionally, it featured expense calculation, income tracking, and the ability to generate reports for tax purposes to be submitted to the Tax Administration.
%	\item Other notable features of the software included hardware lock protection and file management for real estate consultants.
%	\item Each real estate consultant had a personalized user area on the web page, requiring activation of the software through a serial number and password, which had to be registered in their user area.
%	\item The web panel was developed using PHP for the back-end and JavaScript for the front-end.
%	\item The Sama software remained active for several years in provinces such as Khuzestan, Alborz, and certain areas of Tehran.
    \end{subsection}


 \begin{subsection}{Amoozesheyar (Educational Website)}{Teaching}{Mar 2014 - Aug 2014}{Remote , Iran}{(Educational Website)}
	\item Created and delivered instructional content on web design and programming, with a particular focus on WordPress theme development and customization, including comprehensive tutorials on setting up a WordPress-based blogging system, a unique offering in Iran at that time.
	%\item Engaged in teaching and instructing web design, programming, and implementing WordPress themes on the Amoozesheyar website.
	%\item Provided tutorials on setting up a blogging system using WordPress, which was a unique offering in Iran during that time.
	%\item Published instructional materials on the website during this period.
	\item Part 1:  \href{https://www.daneshjooyar.com/%d9%82%d8%b3%d9%85%d8%aa-%d9%86%d9%87%d8%a7%db%8c%db%8c-%d8%b3%d8%b1%db%8c-%d8%a2%d9%85%d9%88%d8%b2%d8%b4%db%8c-%d8%b7%d8%b1%d8%a7%d8%ad%db%8c-%d9%82%d8%a7%d9%84%d8%a8-%d9%88%d8%b1%d8%af%d9%be%d8%b1/}{Link to the published tutorials on WordPress theme design} 
	\item Part 2: \href{https://www.daneshjooyar.com/%d8%a2%d9%85%d9%88%d8%b2%d8%b4-%d8%b7%d8%b1%d8%a7%d8%ad%db%8c-%d9%82%d8%a7%d9%84%d8%a8-%d9%88%d8%b1%d8%af%d9%be%d8%b1%d8%b3-%d8%aa%d9%85%d8%a7%d9%85%db%8c-%d9%82%d8%b3%d9%85%d8%aa-%d9%87%d8%a7-%d9%82/}{Link to the complete tutorials on WordPress theme design}
    \end{subsection}
    
\end{section}



\begin{section}{Projects}
    \begin{subsection}{MrOlympiad}{Full-Stack Developer}{Apr 2019 - Nov 2020}{Contract}{}
%     		\item Full-stack development using PHP, JavaScript, jQuery, and MySQL.
%		\item The MrOlympiad website serves as a question bank and online exam platform for student Olympiads.
%		\item The implementation of this website began in early 2019 and was completed in two phases: question bank and online exams by the end of 2020.
%		\item Key features of the website include the sale of question packages, automatic exam generation using the question bank repository, personalized question categorization by students, and providing a panel for educational institutions to manage students and conduct online exams.
%		\item Upon the website's initial launch, approximately 1,000 registrations were recorded. Today, MrOlympiad is widely recognized and popular among student Olympians
		\item Full-Stack development of the MrOlympiad platform using PHP, JavaScript, jQuery, and MySQL, focusing on creating a robust online exam and question bank system for student Olympiads.
		\item Designed and implemented key features, including a question bank, automatic exam generation, and personalized question categorization, catering to both students and educational institutions.
		\item Managed the project in two phases: development of the question bank and implementation of online exam functionalities, completing the project by the end of 2020.
%		\item Developed a comprehensive panel for educational institutions to manage students and conduct exams efficiently.
		\item Achieved initial success with around 3,000 registrations at launch, contributing to the platform's growing recognition and popularity among student Olympians.
    \end{subsection}
    \begin{subsection}{Zama Chain Clothing Store Management Software}{Full-Stack Developer}{Apr 2022 - Aug 2022}{Contract}{}
     		\item Developed a web application for a chain of clothing stores with five active branches.
		\item The software included various features such as invoice generation, branch expense tracking, employee assistance recording, inventory management, stock rotation, sending discount codes to customers, customer loyalty program, profit and loss calculation, sending notifications for product depletion in stores or warehouses, employee salary calculation, and more.

    \end{subsection}

\begin{subsection}{Management Portal for Karaj Startup House}{Full-Stack Developer}{Jul 2022 - 2023 Feb}{Contract}{}
     		\item Developed a comprehensive management portal for Khaneh Startup Karaj, a co-working space located in Alborz province.
		\item Recognizing the challenges arising from the increasing population within the environment and the need for more efficient management of the pre-accelerator, the management portal was designed to cater to the specific needs of the members.
		\item The portal covers all processes, starting from the moment a team or individual enters the complex until their departure, providing a seamless experience throughout their stay.
		\item Implemented features that streamline various tasks such as registration, access management, resource allocation, event scheduling, and communication within the community.
		\item Improved the overall efficiency of operations by automating manual processes and providing a centralized platform for members to access relevant information and services.
		\item Collaborated closely with the Khaneh Startup Karaj team to gather requirements, design user-friendly interfaces, and ensure seamless integration with existing systems.
    \end{subsection}


    
\end{section}


\sectiontable{Technical skills}{
    \entry{Programming Languages}{PHP, Java}
    \entry{Web Development}{HTML, CSS, JavaScript, jQuery, Angular, Symfony}
    \entry{Databases}{MySQL, ORACLE}
\entry{Frameworks}{Spring Boot,  Symfony}
    \entry{Version Control}{Git}
	\entry{Project Management}{Agile methodologies (Scrum)}
%\entry{Soft}{Problem Solving and Analytical Thinking , Strong Communication and Collaboration Skills}
}


\sectiontable{Awards \& Coursework}{
 \entry{Digikala Educational Cup Competition }{Third Place \hfill \textit{2020}}
    \entry{PHP Certificate}{Quera College - Perfect Score - \href{https://quera.org/certificate/OYWeHltR/}{link} \hfill \textit{2020}}
\entry{Winter Camp, DigiNext}{Advanced tech and skills development. \hfill \textit{Winter 2022}}
}


\begin{section}{Education}

   \begin{subsectionnobullet}{Bachelor of Computer Engineering}{Specialization: Software Engineering}{Azad University-2024}{}
        \italicitem{}
    \end{subsectionnobullet}
    
\end{section}

\end{document}


